---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---


{r, message = False}
library(knitr)
opts_chunk$set(message = False, warnings = False)

%>%pipe syntax is to avoid storing intermediate computations.


```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```


[Olympics Derivations] This problem gives some practice with deriving and visualizing new variables.

```{r}
olympics <- read.csv("https://uwmadison.box.com/shared/static/rzw8h2x6dp5693gdbpgxaf2koqijo12l.csv")
olympics
```

a. Create new columns for the city and country of birth for each athlete in the
London 2012 Olympics
[dataset](https://uwmadison.box.com/s/rzw8h2x6dp5693gdbpgxaf2koqijo12l).

```{r}
colnames(olympics)
```


```{r}
olympics %>%
  mutate(city = str_split(`Place.of.birth`, "\\(")) %>%
  dplyr::select(Name, `Place.of.birth`, city) %>%
  unnest_wider(city, "_")%>%
  select(-city_2)%>%
  rename(city = city_1)

```

b. Compute the standard deviation of athlete age within each sport. Which sport
has widest SD in age?

```{r}
olympics %>%
  group_by(Sport) %>%
  summarise(age_sd = sd(Age))
  filter(age_sd == max(age_sd, na.rm = TRUE))
```

c. Make a visualization of sports against participant age. Sort sports by
age variance.

```{r}
olympics_count <- olympics %>%
  count(Sport)

olympics %>%
  left_join(olympics_count) %>%
  filter(n > 4)
  ggplot()+
      geom_boxplot(aes(Age, reorder(Sport, Age, sd)))

```


```{r, fig.width=8, fig.height=10}
ggplot(olympics) +
  geom_boxplot(aes(Age, reorder(Sport, Age, sd)))
```

```{r}
olympics %>%
  group_by(Sport) %>%
  mutate(n = n()) %>%
  filter(n > 4) %>%
  ggplot() +
  geom_boxplot(aes())
```

