---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```


[Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.

```{r}
library(tidyverse)
plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
plants
```

a. Propose an alternative arrangement of rows and columns that conforms to the
tidy data principle.
| treatment | plant_id | time | height
```{r}

```


b. Implement your proposed arrangement from part (a).

```{r}
plants %>%
  pivot_longer(c("height.0","height.7","height.14","height.21"))
plants_long <- plants %>%
  pivot_longer(starts_with("height")) %>%
  mutate(
    day = str_extract(name, "[0-9]+"),
    day = as.integer(day)
    )
  
plants_long
  
```
geom_line(aes(name, value)) +
facet_wrap(~ treatment)

```{r}
ggplot(plants_long, aes(day, value, col = treatment)) +
  geom_point() +
  geom_line(aes(group = plantid)) +
  facet_wrap(~treatment)
```



c. Using the dataset from (b), design and implement a visualization showing the
growth of the plants over time according to different treatments.


//////////////
```{r}
library(nycflights13)
flights %>% select(carrier, air_time, distance)
flight %>%
  mutate(speed = distance/air_time) %>%
  ggplot() +
  geom_boxplot(aes(speed, reorder(carrier, speed, median, na.rm = 1)))


```

